Solution of near-Toeplitz tridiagonal systems on GPU-accelerated clusters

### 2016-03-17 paper-draft/paper.tex
Address Mattor et al. argument about CR/Thomas algorithm

\hl{
Thus, cyclic reduction requires \emph{significantly} fewer steps
($2log_2(n) - 1$) compared to Thomas algorithm ($2n$).
Each step in cyclic reduction consists of operations on several indices
that can each be done in parallel,
making it a good fit for massively parallel architectures such as GPUs.}

>>>>

\hl{
Thus, cyclic reduction requires \emph{significantly} fewer steps
($2log_2(n) - 1$) compared to Thomas algorithm ($2n$).
Each step in cyclic reduction consists of operations on several indices
that can each be done independently,
suggesting a parallel (multi-threaded) approach.
When solving linear systems with the same matrix but several right hand sides,
a thread-parallel Thomas algorithm in which
each thread solves an independent system may be considered.
Mattor et al. suggest that this may be a more efficient use
of parallelization compared to cyclic reduction,
due to the smaller amount of work required per thread.
However, using cyclic reduction for solving the independent systems
exposes a larger amount of parallelism -
which is important for good performance on GPUs.
When the number of systems to be solved is small
(as is the case in 2-D problems and small 3-D problems),
the thread-parallel Thomas algorithm under-utilizes the GPU.
For larger problems,
successive threads access far-apart memory locations,
leading to poor GPU performance.
Thus, we argue that cyclic reduction is a better fit for
massively parallel architectures such as GPUs.
}
